---
title: "R Notebook"
output: html_notebook
---

# **Spaceship Titanic**

```{r}
data1 <- read_csv('sample_submission.csv')
data2 <- read_csv('test.csv')


```

Join Data1 and Data2

```{r}
df <- merge(x=data1 , y =data2 , by.x = "PassengerId", by.y = "PassengerId")
View(df)
```

Creating column name group from PassengerId

```{r}
data <- mutate(df, group = substr(
PassengerId,1,4))


View(data)

```

Counting the occurrences of each value in the Transported column.

```{r}
value <-  count(data, Transported)
value

#No one from this dataset has been transported to another dimension.
```

```{r}
ggplot(value, aes(x="", y=n, fill=Transported)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)
```

Checking if there is any TRUE value

```{r}
trnsported_true <- filter(data, Transported == TRUE)
trnsported_true
```

The oldest person aboard the Titanic

```{r}

View(arrange(data, desc(Age)) %>%
  slice(1))
```

Which group has the oldest average age with at least 2 members?

```{r}


group_age <- data %>%
  group_by(group)%>%
  summarise(
    mean_age = mean(Age, na.rm=TRUE),
    n=n()
  )%>%
  filter(n>=2)%>%
  arrange(desc(mean_age))%>%
  slice(1)
print(group_age)

#3580 group has the oldest average age of 64 with at least 2 members		
```

find the vips

```{r}

Vip <- filter(data, VIP == TRUE)
View(Vip)
```

Most popular home planet for Vips

```{r}
group_by(Vip, HomePlanet) %>%
  summarise(
    n = n()
  )
#most comman Home planet for Vips are Eruopa with 46 people
```

Which group has the highest average bill for luxury amenities?

```{r}
luxury_bill <- data %>%
  group_by(VIP)%>%
  summarise(
    agv.RS_bill = mean(RoomService, na.rm=TRUE),
    avg.Food_bill = mean(FoodCourt, na.rm =TRUE),
    avg.spa_bill =mean(Spa,na.rm=TRUE),
    avg.SM_bill = mean(ShoppingMall,na.rm=TRUE),
    avg.VR_bill = mean(VRDeck, na.rm = TRUE)
  )

View(luxury_bill)

#Vip has the highest bill in luxury amanities.
```

What is the avg age for different homeland

```{r}
group_by(data, HomePlanet)%>%
  summarise(avg.age = mean(Age,na.rm=TRUE),
            count = n())

#avg age for different homeland 
#Earth	25.74617	 	
#Europa	34.15886 	
#Mars	29.76281	 
```

Where are most people from Earth traveling to

```{r}
group_by(data, HomePlanet, Destination) %>%
summarise(
          count =n()) %>%
  filter(HomePlanet == 'Earth')%>%
  arrange(desc(count)) %>%
  slice(1)

# most people from Earth traveling toTRAPPIST-1e
```

What do people spend the most money on in the year 2912

```{r}
summarise(data,
    agv.RS_bill = mean(RoomService, na.rm=TRUE),
    avg.Food_bill = mean(FoodCourt, na.rm =TRUE),
    avg.spa_bill =mean(Spa,na.rm=TRUE),
    avg.SM_bill = mean(ShoppingMall,na.rm=TRUE),
    avg.VR_bill = mean(VRDeck, na.rm = TRUE)
  )

#What do people spend the most money on in the year 2912  avg.Food_bill


```

```{r}
ggplot(data =  data) +
  geom_point(mapping = aes(x = Age, y = FoodCourt, color= HomePlanet))

#The graph shows that people start spending money in the food court around the age #of 17, and people from Europe are the heaviest spenders on food.
```

## Hypothesis

-   No one from this dataset has been transported to another dimension.

-    The oldest person on the Titanic was 79 years old."

-   "Group 3580 has the oldest average age of 64 with at least 2 members."

-   "The most common home planet for VIPs is Europa, with 46 people."

-   "VIPs have the highest bill in luxury amenities."

-   "The average age for different homelands is: Earth 25.74617, Europa 34.15886, Mars 29.76281."

-   "Most people from Earth are traveling to TRAPPIST-1e."

-   "People spend the most money on average on food bills in the year 2912."

-   "The graph shows that people start spending money in the food court around the age of 17, and people from Europe are the heaviest spenders on food.
